Body Image and Trikafta

### 2023-01-13 Emily Muther/body_image_trikafta.qmd
Update body_image_trikafta.qmd

```{r}
#| include: false
# Libraries
library(haven)
library(tidyverse)
library(arsenal)
# Import
df = read_sav("Z:/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Body Image and Trikafta/Data_Raw/TrikaftaBodyImage1.11.23.sav")
# Format variables
df$`Percent Adherence` = factor(df$PercentAdherence,levels = 1:11,
                             labels = paste0(seq(0,100,by=10),"%"),ordered = T)
df$`FRS Category` = factor(df$FRS_Category,levels = -1:1,
                           labels = c("want to be larger","neutral",
                                      "want to be smaller"))
df$`Doses Missed` = as.numeric(df$DosesMissed)
df$`Weight/Body Adherence` = factor(df$WeightBody_Adherence,levels = 1:5,
               labels = c("Strongly Agree","Slightly Agree","Neutral",
                          "Slightly Disagree","Strongly Disagree"))
df$`Weight/Body Adherence` = fct_rev(df$`Weight/Body Adherence`)
df$`Weight/Body Adherence` = factor(df$`Weight/Body Adherence`,ordered = T)
```

@@

```{r results='asis'}
#| label: tbl-1
#| tbl-cap: Comparisons by FRS Category
t1 = tableby(`FRS Category`~kwt(`Percent Adherence`)+`Doses Missed` +
               kwt(`Weight/Body Adherence`),data = df,
             control=tableby.control(numeric.stats=c("Nmiss","median","q1q3","range"),
                                     numeric.test="kwt"))
summary(t1,pfootnote = T)
```

```{r}
#| label: fig-planets
#| fig-cap: Planets

```

>>>>

```{r}
#| include: false
# Libraries
library(knitr)
library(kableExtra)
library(haven)
library(tidyverse)
library(arsenal)
library(psych)
library(ggcorrplot)
# Import
df = read_sav("Z:/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Body Image and Trikafta/Data_Raw/TrikaftaBodyImage1.11.23.sav")
# Format variables
df$`Percent Adherence` = factor(df$PercentAdherence,levels = 1:11,
                                labels = paste0(seq(0,100,by=10),"%"),ordered = T)
df$`FRS Category` = factor(df$FRS_Category,levels = -1:1,
                           labels = c("want to be larger","neutral",
                                      "want to be smaller"))
df$`Doses Missed` = as.numeric(df$DosesMissed)
df$`Weight/Body Adherence` = factor(df$WeightBody_Adherence,levels = 1:5,
                                    labels = c("Strongly Agree","Slightly Agree","Neutral",
                                               "Slightly Disagree","Strongly Disagree"))
df$`Weight/Body Adherence` = fct_rev(df$`Weight/Body Adherence`)
df$`Weight/Body Adherence` = factor(df$`Weight/Body Adherence`,ordered = T)
df$`Do Not Want Trikafta` = factor(df$DoNotWantTrikafta,levels = 1:6,
                                   labels = c("Strongly Agree","Slightly Agree",
                                              "Neutral","Slightly Disagree",
                                              "Strongly Disagree",NA))
df$`Do Not Want Trikafta` = fct_rev(df$`Do Not Want Trikafta`)
df$`Do Not Want Trikafta` = factor(df$`Do Not Want Trikafta`,ordered = T)
df$`Continue Trikafta` = factor(df$ContinueTrikafta,levels = 0:6,
                                labels = c(NA,"Strongly Agree",
                                           "Slightly Agree","Neutral",  
                                           "Slightly Disagree","Strongly Disagree",NA))
df$`Continue Trikafta` = fct_rev(df$`Continue Trikafta`)
df$`Continue Trikafta` = factor(df$`Continue Trikafta`,ordered = T)
```

@@

```{r results='asis'}
#| label: tbl-1
#| tbl-cap: Comparisons by FRS Category
rh = "~kwt(`Percent Adherence`)+`Doses Missed`+kwt(`Weight/Body Adherence`)+kwt(`Do Not Want Trikafta`)+kwt(`Continue Trikafta`)"
t1 = tableby(as.formula(paste0("`FRS Category`",rh)),data = df,
             control=tableby.control(numeric.stats=c("Nmiss","median","q1q3","range"),numeric.test="kwt"))
summary(t1,pfootnote = T)
```

```{r results='asis'}
#| label: tbl-2
#| tbl-cap: Spearman's Rho
x = df %>% select(BE_APPEARANCE_MEAN:BE_ATTRIBUTION_MEAN) %>% data.matrix(.)
y = df %>% select(`Percent Adherence`:`Continue Trikafta`) %>% data.matrix(.)
r = corr.test(x,y,adjust = "fdr")
kable(r$r,digits=3)
```

```{r results='asis'}
#| label: tbl-3
#| tbl-cap: Spearman's Rho FDR-Adjusted p-values
kable(r$p,digits=3)
```

```{r}
#| label: fig-heat
#| fig-cap: Correlation Heatmap
ggcorrplot(r$r,p.mat = r$p.adj)
```
